Flexible Binary Instrumentation for the Kernel

### 2013-11-11 VEE-14/paper.tex
Minor change to a figure

% Code block showing an example JZ (jump if ZF=1).
\lstset{language=[x64]Assembler}
\newsavebox\nativejcc
\begin{lrbox}{\nativejcc}
\begin{minipage}[b]{4cm}
\begin{lstlisting}[basicstyle=\footnotesize\ttfamily]
cmp $0x0, %rax
jz value_is_zero 
...
( fall through )
\end{lstlisting}
\end{minipage}
\end{lrbox}

\newsavebox\translatedjcc
\begin{lrbox}{\translatedjcc}
\begin{minipage}[b]{4cm}
\begin{lstlisting}[basicstyle=\footnotesize\ttfamily]
  cmp $0x0, %rax
jz_to_patch:
  jmp edge_value_is_zero
  ...
edge_value_is_zero:
  ( spill 2 registers )
  ( save value_is_zero )
  ( save target policy )
  call patcher_for_jz
  ( restore 2 registers )
  jmp .jz_to_patch
\end{lstlisting}
\end{minipage}
\end{lrbox}

>>>>

% Code block showing an example JZ (jump if ZF=1).
\lstset{language=[x64]Assembler}
\newsavebox\nativejcc
\begin{lrbox}{\nativejcc}
\begin{minipage}[b]{4cm}
\begin{lstlisting}[basicstyle=\footnotesize\ttfamily]cmp $0x0, %rax

jz value_is_zero 
...

( fall through )
\end{lstlisting}
\end{minipage}
\end{lrbox}

\newsavebox\translatedjcc
\begin{lrbox}{\translatedjcc}\begin{minipage}[b]{4cm}\begin{lstlisting}[basicstyle=\footnotesize\ttfamily]  cmp $0x0, %rax
jz_to_patch:
  jmp edge_value_is_zero
  ...
edge_value_is_zero:
  ( spill 2 registers )
  ( save value_is_zero )
  ( save target policy )
  call patcher_for_jz
  ( restore 2 registers )
  jmp .jz_to_patch
\end{lstlisting}
\end{minipage}
\end{lrbox}
